Time scales for cline flattening

### 2015-12-03 notes/time-scales.Rmd
.

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r fwds_soln_plot, cache=TRUE, depends="setup_tens"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```

@@

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r fwds_soln_plot, cache=TRUE, depends="setup_hunds"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```

@@

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r fwds_soln_plot, cache=TRUE, depends="setup_thous"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```

>>>>

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r tens_fwds_soln_plot, cache=TRUE, depends="setup_tens"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```

@@

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r hunds_fwds_soln_plot, cache=TRUE, depends="setup_hunds"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```

@@

Here's the behaviour of the selected site that we use to describe the behaviour of the other sites:
```{r thous_fwds_soln_plot, cache=TRUE, depends="setup_thous"}
image(fwds.soln, legend=TRUE, zlim=c(0,1), yaxt='n', main="selected site", ylab="space")
add_grid_axis(xgrid)
```
